---
title: "ReadMe"
author: Jose Baltazar
output: html_document
---

# Dataset and motivation

This report analyses a data set containing data regarding the elemental composition of cannabis leaves 
grow in 3 different soils of New Zealand. The exploratory analysis aims to answer the following questions:

- Do the data indicate differences in the elemental composition of the cannabis leaves grown in 
different soil types?
- Are some of the elements related to one another in terms of their levels in the samples leaves?

# Packages

The packages used to complete this project were the following:
```{r, echo=FALSE}
library(NCmisc)
list.functions.in.file("C:/Users/josep/Documents/GitHub/Weed/Weed.R")
```

# Conclusion

- The data indicate differences in the elemental compositions of leaves grown in different soil types. By knowing the concentration of a certain element, one could identify in which soil the plant has grown. 

```{r, echo=FALSE}
#importing sheet1 and cleaning data
sheet1 <- read_excel("C:/Users/josep/Desktop/Srishdata/PotPlants_18.xlsx", sheet = 'SampleSetOne')
#changing "Sample.Name" to "Sample Name"
sheet1 <- (setnames(sheet1, old = c("Sample,Name"), new =c("Sample Name")))

#importing sheet2 and cleaning data
sheet2 <- read_excel("C:/Users/josep/Desktop/Srishdata/PotPlants_18.xlsx", sheet = 'SampleSetTwo')

#replacing potting mix with pm
sheet2 <- sheet2 %>% mutate(Group = recode(Group, 'potting mix' = 'pm'))
#removing NA's
sheet2<- sheet2%>%na.omit
#removing mean and variance values at the bottom
sheet2 <- (sheet2[-c(53,54),])
#changing "SampleName" to "Sample Name"
sheet2 <- (setnames(sheet2, old = c("SampleName"), new =c("Sample Name")))

#importing sheet3 and cleaning data
sheet3 <- read_excel("C:/Users/josep/Desktop/Srishdata/PotPlants_18.xlsx", sheet = 'SampleSetThree')
#remove "missing" values
sheet3 <- (sheet3[-c(49),])
#converting the elements from factor to numbers.
sheet3 <- mutate_at(sheet3, vars(-Sample.Name, -Group), function(x) as.numeric(as.character(x)))
#changing "Sample.Name" to "Sample Name"
sheet3 <- (setnames(sheet3, old = c("Sample.Name"), new =c("Sample Name")))

#combining all the sheets into one data set
sheet <- rbind(sheet1, sheet2, sheet3)


#ANALYSIS
#question 1
#Do the data indicate differences in the elemental composition of the cannabis leaves grown in 
#different soil types?
  

#Creating a function "test" to filter the data set and show only the elements I want to analize for question 1.
test <-  sheet [c("Group", "Mg", "Al", "K", "Ca", "Sc")]

#"newData" is a new function arranges the data in "test"
newData <- test %>% gather(key = Element, value = Measure, Mg, Al, K, Ca, Sc)

ggplot(data = newData) + geom_point(aes(x = Element, y = Measure, colour = Element )) + facet_grid(~ Group)
ggplot(data = newData) + geom_boxplot(aes(x = Element, y = Measure, colour = Element )) + facet_grid(~ Group)
```

- 